Towards a miniKanren with fair search strategies

### 2019-05-28 Paper/paper.tex
a few more corrections

miniKanren is a family of relational programming languages.
\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \mbox{\citet{Hemann_2016}}
describe microKanren, a minimal core of miniKanren comprised of only 54 LOC, 
miniKanren has been implemented in many other languages, including
multiple ones using the same language (e.g. OCanren\citep{kosarev2018typed}). 
\citet{byrd2017unified} have demonstrated that miniKanren problems that at 
first reading seem impossible are indeed possible by using a Scheme interpreter 
written in miniKanren, thereby having access to logic variables within Scheme.
miniKanren.org contains links to many miniKanren implementations and the seeds 
of many interesting problems and their solutions.

>>>>

miniKanren is a family of relational programming languages.
\citet{Friedman:2005:RS:1121583,friedman_reasoned_2018} introduce
miniKanren and its implementation in \emph{The Reasoned Schemer} 
and \emph{The Reasoned Schemer, 2nd Ed} (TRS2). After \mbox{\citet{Hemann_2016}}
describe microKanren, a minimal core of miniKanren comprised of only 54 LOC, 
miniKanren has been implemented in many other languages, including
multiple ones using the same language (e.g. OCanren\citep{kosarev2018typed}). 
% \citet{byrd2017unified} have demonstrated that miniKanren problems that at 
% first reading seem impossible are indeed possible by using a Scheme interpreter 
% written in miniKanren, thereby having access to logic variables within Scheme.
As demonstrated in \citet{byrd2017unified}, miniKanren can be used to
naturally express difficult computations, such as using an interpreter
to perform example-based program synthesis, or using a proof checker
as a theorem prover.
% miniKanren.org contains links to many miniKanren implementations and the seeds 
% of many unusual problems and their solutions in miniKanren.
The papers, talks, and tutorials on \url{miniKanren.org} present many
other unusual problems, and their solutions in miniKanren.
